### 2014-02-28 paper/concrete.tex
checkpoint.

A na\"ive attempt at our single heap semantics
will not allow us to construct an isomorphism
with the abstract language |specLangML alpha|, and instead highlights
where things will go wrong.

>>>>

A na\"ive attempt at our single heap semantics
will not allow us to construct an isomorphism
with the abstract language |specLangML alpha|, and instead highlights
where things will go wrong.
To successfully construct an isomorphism, our concrete semantics need
to mirror the behavior of the abstract semantics, most importantly
in the case where tasks interact.  Namely, at a fork and when sending
or receiving messages, we take an expression from one task and
execute it in the context of another task.  In the abstract semantics
the fork rule
